%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%\documentclass[12pt, a4paper]{article}
\documentclass[12pt]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
%\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\geometry{textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
%\setmainfont[
%  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
%  BoldFont=LinLibertine_RB.otf,
%  ItalicFont=LinLibertine_RI.otf,
%  BoldItalicFont=LinLibertine_RBI.otf
%]{LinLibertine_R.otf}
%\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Jeffrey Mulligan - vita},
	pdfauthor={Jeff Mulligan},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

% DOCUMENT
\begin{document}
{\LARGE Jeffrey Brooke Mulligan}\\[1cm]
 Human Systems Integration Division\\
 NASA Ames Research Center\\
MS 262-2\\
Moffett Field, CA \texttt{94035}
\\[.2cm]
Phone: \texttt{650-604-3745} (W), \texttt{408-250-6567} (C)\\
Fax: \texttt{650-604-3323}\\[.2cm]
email: \href{mailto:jeffrey.b.mulligan@nasa.gov}{jeffrey.b.mulligan@nasa.gov}\\
\textsc{url}: \href{http://hsi.arc.nasa.gov/groups/scanpath/}{http://hsi.arc.nasa.gov/groups/scanpath/}\\ 
alt. email: \href{mailto:jbmull@gmail.com}{jbmull@gmail.com}\\
%\vfill
% Born:  December 14, 1958---Detroit, MI\\

%%\hrule
%\section*{Current position}
%%\emph{Emeritus Professor}, Institute for Advanced Study, Princeton
%Computer Engineer (GS 14-10), NASA Ames Research Center

%%%\hrule
%\section*{Skills}
% Psychophysical research • Optics • Electronic design • Computer programming

%\hrule
\section*{Education}
\noindent
\years{1986}\textsc{PhD} in Psychology, University of California at San Diego\\
\years{1982}\textsc{MA} in Psychology, University of California at San Diego\\
\years{1980}\textsc{AB} in Physics (\emph{cum laude} general studies), Harvard University\\
\years{1975}US Math Olympiad Summer Program, Rutgers University\\

%%\hrule
\section*{Employment}
\noindent
\years{1987-present}Computer engineer, NASA Ames Research Center\\
\years{1986-1987}National Research Council post-doctoral associate, NASA Ames Research Center\\
\years{1980-1986}Research and teaching assistant, Department of Psychology, UC San Diego\\
\years{1982-1983}Research assistant, AT\&T Bell Laboratories, Murray Hill NJ\\
\years{1980}Research assistant, Division of Applied Sciences, Harvard University\\

\section*{Teaching}
\noindent
\years{1991}Introduction to Computer Science, UC Santa Cruz\\
\years{1991}Data Structures, UC Santa Cruz\\
\years{1990}Sensation \& Perception, Cal. State Hayward (Contra Costa campus)\\
\years{1980-1986}Teaching assistant, Department of Psychology, UC San Diego\\
courses taught:  sensory laboratory, neuropsychology

%\hrule
\section*{Professional societies}
\noindent
\years{2001-present}Vision Sciences Society (VSS)\\
\years{1984-present}Optical Society of America (OSA)\\
\years{2005-present}Society for Information Display (SID)\\
\years{1982-2001}Association for Research in Vision and Ophthalmology (ARVO)\\

%\hrule
\section*{Professional service}
\subsection*{Conference organization}
\noindent
\years{2012-present}Co-organizer, VSS satellite workshop on\\
\hspace*{5 mm}Computational and Mathematical Models in Vision (MODVIS)\\
\years{2018-present}Co-chair, IS\&T Conference on Human Vision and Electronic Imaging (HVEI)\\
\years{2004-2018}Program committee, SPIE/IS\&T Conference on\\
\hspace*{5 mm}Human Vision and Electronic Imaging\\
\years{2013-2016}Chair, Vision technical committee, Vision and Color division,  OSA\\
\years{2015}Chair, local organizing committee, OSA Fall Vision Meeting\\
\years{2009-2010,2018}Area chair, ACM Symposium on Eye Tracking Research and Applications\\
\years{2011-2014}Program co-chair, ACM Symposium on Eye Tracking Research and Applications\\
\years{2010-2013}Vice-chair, Vision technical committee, Vision and Color division,  OSA\\
\years{2005-present}Program committee (Applied Vision subcommittee)\\
\hspace*{5 mm}Society for Information Display\\
\years{2006-present}Program committee, International Symposium on Visual Computing\\

\subsection*{Standards committees}
\years{2017-present}International Committee for Display Metrology\\
\years{2013-present}COGAIN technical committee for eye tracker data quality standardization\\

\subsection*{\emph{Ad hoc} reviewing}
Journal of Vision (``exceptional reviewer")\\
Vision Research\\
Journal of the Optical Society of America, A\\
Displays\\
Biomedical Optics Express\\
IEEE Transactions on Biomedical Engineering\\
Physiological Measurement\\
%Optics Letters\\
%Journal of Parallel and Distributed Computing\\
%Journal of Aircraft\\

%\hrule
\section*{Honors \& awards}
\noindent
\years{2018}NASA group achievement award, fatigue app.\\
\years{2016, 2013}NASA software release award\\
\years{2009}NASA group achievement award, Constellation Training Facility team\\
\years{1983-1985}IBM graduate fellowship\\
\years{1984}NIH travel scholarship to attend International School of Biophysics (Italy)\\
\years{1983}ARVO travel fellowship\\


%\vspace{10 mm}

%\clearpage
\section*{Software}
\years{2009,2016}
QuIP - An interactive environment for QUick Image Processing.  The QuIP interpreter provides a convenient interface to libraries for image processing, graphics, image acquisition, and control of other pieces of laboratory hardware.  The systems runs on unix-like systems (linux, Mac OSX), and Apple iOS.  GPU acceleration is provided with either CUDA or OpenCL.\\
\href{https://github.com/nasa/QuIP}{https://github.com/nasa/QuIP}

\section*{Publications}


\subsection*{Journal articles (17) \& proceedings papers (32)}
\noindent

\years{2018}
Mulligan, J. B. (2018).  ``Statistical identifications of fixations in noisy eye movement data." in Rogowitz, B. E. Pappas, T. N., and de Ridder, H. (eds.), \emph{Human Vision and Electronic Imaging 2018, IS\&T International Symposium on Electronic Imaging 2018}.\\

\years{2017}
Arsintescu, L., Mulligan, J. B., and Flynn-Evans, E. E. (2017).
``Evaluation of psychomotor vigilance task for touch screen devices."
\emph{Human Factors},
\newline
DOI:10.1177/0018720816688394.
\href{https://hsi.arc.nasa.gov/publications/Arsintescu_Mulligan_Flynn-Evans_pvt.pdf}{PDF}
\\

\years{2016}
Mulligan, J. B. (2016).  ``A method for rapid measurement of contrast sensitivity on mobile touch-screens." in Rogowitz, B. E. Pappas, T. N., and de Ridder, H. (eds.), \emph{Human Vision and Electronic Imaging 2016, IS\&T International Symposium on Electronic Imaging 2016},  pp. HVEI-104.1 - HVEI-104.6.  \href{https://hsi.arc.nasa.gov/publications/Mulligan_HVEI_2016_Rapid_Meas_Mobile.pdf}{PDF}\\

\years{2013}
Mulligan, J. B., Stevenson, S. B., and Cormack, L. K. (2013).
``Reflexive and voluntary control of smooth eye movements.”
in Rogowitz, B. E. Pappas, T. N., and de Ridder, H. (eds.),
\emph{Human Vision and Electronic Imaging XVIII},
Proc. SPIE, v. 8651.  \href{https://hsi.arc.nasa.gov/publications/mulligan_et_al_spie13.pdf}{PDF}\\

\years{2012}
Mulligan, J. B. (2012).
``A GPU-accelerated software eye tracking system.”
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA),
pp. 265-268.  \href{https://hsi.arc.nasa.gov/publications/mulligan_etra12.pdf}{PDF}\\

% clearpage forces a page break - we do this so citations
% don't straddle page breaks - but these have to be placed by hand!?
%\clearpage

\years{2010}
Mulligan, J. B., and Gabayan, K. N. (2010).
``Robust optical eye detection during head movement.”
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA),
pp. 129-132.  \href{https://hsi.arc.nasa.gov/publications/mulligan_gabayan_etra10.pdf}{PDF}\\

McDermott, K. C., Malkoc, G., Mulligan, J. B., and Webster, M. A. (2010).
``Adaptation and visual salience."
\emph{J. Vis.}, v. 10(13), pp. 1-32.\\

\years{2009}
Mulligan, J. B. (2009).
``Presentation of calibrated images on the web.”
in Rogowitz, B. E. and Pappas, T. N. (eds.),
\emph{Human Vision and Electronic Imaging XIV},
Proc. SPIE, v. 7240.  \href{https://hsi.arc.nasa.gov/publications/mulligan_spie09.pdf}{PDF}\\

Ahumada, A. J., Jr., Kaiser, M. K., and Mulligan, J. B. (2009).
``The dynamic range of visual imagery in space.”
in Rogowitz, B. E. and Pappas, T. N. (eds.),
\emph{Human Vision and Electronic Imaging XIV},
Proc. SPIE, v. 7240.\\

Mulligan, J. B. (2009)
``Motion parallax enhances depth in a perspective air-traffic display."
\emph{SID Symposium Digest of Technical Papers}, v. 40(1), pp. 1231-1233.  \href{https://hsi.arc.nasa.gov/publications/mulligan_sid09.pdf}{PDF (check)}\\
% make sure sid09 paper is really on the site?  BUG

\years{2008}
Mulligan, J. B. (2008).
``Measurement of eye velocity using active illumination.”
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA),
pp. 35-38.  \href{https://hsi.arc.nasa.gov/publications/mulligan_etra08.pdf}{PDF}\\

\years{2006}
Mulligan, J. B. (2006).
``Optical eye models for gaze tracking.”
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA), p. 51.  \href{https://hsi.arc.nasa.gov/publications/mulligan_etra06.pdf}{PDF}\\

McDermott, K., Mulligan, J. B., Bebis, G., and Webster, M. A. (2006).
``Visual search and eye movements in novel and familiar contexts.”
in Rogowitz, B. E., Pappas, T. N., and Daly, S. J. (eds.),
\emph{Human Vision and Electronic Imaging XI},
Proc. SPIE, v. 6057.\\

\years{2005}
Mulligan, J. B. (2005).
``A tree-structured model of visual appearance applied to gaze-tracking."
In Bebis, G., Boyle, R., Koracin, D., and Parvin, B. (eds.),
\emph{First International Symposium on Visual Computing},
Springer Lecture Notes on Computer Science v. 3804, pp. 303-312.  \href{https://hsi.arc.nasa.gov/publications/mulligan_isvc05.pdf}{PDF}\\

\clearpage
Mulligan, J. B., and Brolly, X. L. C. (2005).
``Pilot behavior and course deviations during precision flight.”
in Rogowitz, B. E. and Pappas, T. N. (eds.),
\emph{Human Vision and Electronic Imaging X},
Proc. SPIE, v. 5666,
pp. 362-373.  \href{https://hsi.arc.nasa.gov/publications/mulligan_spie05.pdf}{PDF}\\
% Human Vision and Electronic Imaging X, pp.  362-373.

\years{2004}
Mulligan, J. B., and Brolly, X. L. C. (2004).
``Surface determination by photometric ranging."
\emph{Conference on Computer Vision and Pattern Recognition Workshop} (CVPRW04),
v. 3, pp. 40-47.  \href{https://hsi.arc.nasa.gov/publications/Mulligan_Brolly_ranging.pdf}{PDF}\\

Brolly, X. L. C., and Mulligan, J. B. (2004).
``Implicit calibration of a remote gaze tracker."
\emph{Conference on Computer Vision and Pattern Recognition Workshop} (CVPRW04),
v. 8, pp. 134-141.  \href{https://hsi.arc.nasa.gov/publications/Brolly_Mulligan_galvo.pdf}{PDF}\\

Meyer, G. F., Mulligan, J. B., and Wuerger, S. M. (2004).
``Continuous audio-visual digit recognition using N-best decision fusion."
\emph{Information Fusion}, v. 5(2), pp. 91-101.\\

\years{2003}
Brolly, X. L. C., Stratelos, C., and Mulligan, J. B. (2003).
``Model-based head pose estimation for air-traffic controllers."
\emph{Proc. IEEE International Conf. on Image Processing} (ICIP),
Barcelona, Spain, v. 3, pp 113-116.  \href{https://hsi.arc.nasa.gov/publications/mulligan_icip03.pdf}{PDF}\\

\years{2002}
Mulligan, J. B., (2002).
``A software-based eye tracking system for the study of air-traffic displays."
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA),
pp. 69-76.  \href{https://hsi.arc.nasa.gov/publications/mulligan_etra02jbm.pdf}{PDF}\\

Mulligan, J. B., (2002).
``Vision-based approaches to digital halftoning."
\emph{Proc. 55th Annual Conference
of the Society for Imaging Science and Technology},
Portland OR, pp. 1-4.  \href{https://hsi.arc.nasa.gov/publications/mulligan_pics02_jbm.pdf}{PDF}\\

\years{2001}
Mulligan, J. B., (2001).
``Sensory processing delays measured with the eye movement correlogram."
in Kaminski, H. J., and Leigh, R. J. (eds.),
``Neurobiology of eye movements:  from molecules to behavior."
\emph{Annals of the New York Academy of Science}, v. 956, pp. 476-478.\\

\years{1999}
Watson, A. B., Hu, Q. J., McGowan, J. F. III, and Mulligan, J. B., (1999).
``Design and performance of a digital video quality metric."
\emph{Human Vision and Electronic Imaging IV}, 
Proc. SPIE, v. 3644,
pp. 168-174.\\

\years{1997}
Mulligan, J. B., (1997).
``Application of Motion-JPEG to dynamic stimulus presentation."
\emph{Spatial Vision}, v. 11, pp. 19-32.  \href{https://hsi.arc.nasa.gov/publications/Mulligan_m_jpeg.pdf}{PDF}\\

\clearpage
Mulligan, J. B., (1997).
``Image processing for improved eye tracking accuracy."
\emph{Behavior Research Methods, Instrumentation and Computers},
v. 29, pp. 54-65.  \href{https://hsi.arc.nasa.gov/publications/Mulligan_img_eye_track_accuracy.pdf}{PDF}\\

Mulligan, J. B., (1997).
``Application of temporal error diffusion to motion JPEG."
in Rogowitz, B. E. and Pappas, T. N. (eds.),
\emph{Human Vision and Electronic Imaging II},
Proc. SPIE, v. 3016,
pp. 288-295.  \href{http://hsi.arc.nasa.gov/publications/mulligan_spie97.pdf}{PDF}\\

% clearpage forces a page break - we do this so citations
% don't straddle page breaks - but these have to be placed by hand!?
%\clearpage
Mulligan, J. B., (1997).
``Recovery of motion parameters from distortions in scanned images."
in Le Moigne, J. (ed.),
\emph{Proc. Image Registration Workshop},
NASA Goddard Space Flight Center, Greenbelt, Maryland, November 20-21, 1997.
NASA Publication \# CP-1998-206853.  \href{https://hsi.arc.nasa.gov/publications/mulligan_irw97.pdf}{PDF}\\

\years{1996}
Beutter, B. R., Mulligan, J. B., and Stone, L. S., (1996).
``The barberplaid illusion:  plaid motion is biased by elongated apertures."
\emph{Vision Res.}, v. 36, pp. 3061-3075.\\

Mulligan, J. B., (1996).
``When are supercomputers worth the bother?"
\emph{Behavior Research Methods, Instrumentation and Computers},
v. 28, pp. 239-240.\\

\years{1995}
Mulligan, J. B., and Beutter, B. R., (1995).
``Eye-movement tracking using compressed video images."
\emph{Vision Science and its Applications},
1995 Technical Digest Series,
v. 1,
Optical Society of America,
pp. 163-166.\\

\years{1994}
Mulligan, J. B., and MacLeod, D. I. A., (1994).
``In search of an optoretinogram."
\emph{Vision Science and its Applications},
1994 Technical Digest Series,
v. 2,
Optical Society of America,
pp. 167-170.\\

\years{1993}
Mulligan, J. B., (1993).
``Nonlinear combination rules and the perception of motion transparency."
\emph{Vision Res.},
v. 33, pp. 2021-2030.  \href{https://hsi.arc.nasa.gov/publications/Mulligan_nonlinear_combin.pdf}{PDF}\\

%\clearpage
Mulligan, J. B., (1993).
``Methods for spatiotemporal dithering."
\emph{SID International Symposium Digest of Technical Papers},
v. 24, pp. 155-158.\\

Mulligan, J. B., (1993).
``Improving digital halftones by exploiting visual system properties."
in Singh, A. (ed.), Conference record,
\emph{27th Asilomar conference on Signals, Systems and Computers},
IEEE Computer Society Press,
pp. 961-965.  \href{https://hsi.arc.nasa.gov/publications/mulligan_asil93.pdf}{PDF}\\

\years{1992}
Mulligan, J. B., (1992).
``Anisotropy in an ambiguous kinetic depth effect."
\emph{J. Opt. Soc. Am. A},
v. 9, pp. 521-529.  \href{https://hsi.arc.nasa.gov/publications/Mulligan_anis.pdf}{PDF}\\

Mulligan, J. B., and Ahumada, A. J., Jr., (1992).
``Principled halftoning based on human vision models."
in Rogowitz, B. E. (ed.),
\emph{Human Vision, Visual Processing, and Visual Display III},
Proc. SPIE, v. 1666,
pp. 109-121.  \href{https://hsi.arc.nasa.gov/publications/mulligan_spie92.pdf}{PDF}\\

Mulligan, J. B., and Ahumada, A. J. Jr., (1992).
``Principled methods for color dithering based on models of the human visual system."
\emph{SID International Symposium Digest of Technical Papers},
v. 23, pp. 194-197.\\

\years{1991}
Mulligan, J. B. and MacLeod, D. I. A., (1991).
``Visual sensitivity to spatially sampled modulation in human observers."
\emph{Vision Res.}, v. 31, pp. 895-905.  \href{https://hsi.arc.nasa.gov/publications/Mulligan_samp300.pdf}{PDF}\\

Ahumada, A. J., Jr., and Mulligan, J. B., (1991).
``Network compensation for missing sensors."
in Rogowitz, B. E., Brill, M. H., and Allebach, J. P. (eds.),
\emph{Human Vision, Visual Processing, and Visual Display II},
Proc. SPIE, v. 1453,
pp. 134-146.\\

\years{1990}
Stone, L. S., Watson, A. B., and Mulligan, J. B., (1990).
``Effect of contrast on the perceived direction of a moving plaid."
\emph{Vision Res}., v. 30, pp. 1049-1067.\\

Ahumada, A. J., Jr., and Mulligan, J. B., (1990).
``Learning receptor positions from imperfectly known motions."
in Rogowitz, B. E., and Allebach, J. P. (eds.),
\emph{Human Vision and Electronic Imaging:  Models, Methods, and Applications},
Proc. SPIE, v. 1249,
pp. 124-134.\\

Mulligan, J. B., (1990).
``Digital halftoning methods for selectively partitioning
error into achromatic and chromatic channels."
in Rogowitz, B. E., and Allebach, J. P. (eds.),
\emph{Human Vision and Electronic Imaging:  Models, Methods, and Applications},
Proc. SPIE, v. 1249,
pp. 261-270.  \href{https://hsi.arc.nasa.gov/publications/spie90.pdf}{PDF}\\

\years{1989}
Mulligan, J. B., and Stone, L. S., (1989).
``Halftoning method for the generation of motion stimuli."
\emph{J. Opt. Soc. Am.}, v. 6, pp. 1217-1227.  \href{https://hsi.arc.nasa.gov/publications/josa89.pdf}{PDF (check)}\\
% BUG?  is paper reprint present???

%\clearpage
Ahumada, A. J., Jr., and Mulligan, J. B., (1989).
``Learning in interpolation networks for irregular sampling: some convergence properties."
\emph{OSA Topical Meeting on Applied Vision},
1989 Technical Digest Series,  v. 16, pp. WC3-1 - WC3-4.\\

\years{1988}
Mulligan, J. B., and MacLeod, D. I. A., (1988).
``Reciprocity between luminance and dot density in the perception of brightness."
\emph{Vision Res}., v. 28, 503-519.  \href{http://hsi.arc.nasa.gov/publications/vr88.pdf}{PDF (check)}\\

\years{1986}
Mulligan J. B., (1986).
``Optimizing stereo separation in color television anaglyphs."
\emph{Perception}, v. 15, pp. 27-36.\\

Mulligan J. B., (1986).
``Minimizing quantization errors in a digitally controlled CRT."
\emph{Color Res. Appl.} (suppl.), v. 11, pp. S47-S51.\\

\clearpage
\years{1985}
Nakayama K., Silverman G., MacLeod D. I. A., and Mulligan J. B., (1985).
``Sensitivity to shearing and compressive motion in random dots."
\emph{Perception}, v. 14, pp. 225-238.\\

\years{1982}
Stromeyer C. F. III, Mulligan J. B., Birch D. G., and Dawson B. M., (1982).
``Adaptation to polarized light in humans."
\emph{Vision Res.}, v. 22, pp. 217-224.\\

\subsection*{Book Chapters}
\noindent

\years{2016}  Mulligan, J. B. (in press).  ``Illusory variations in apparent dot brightness induced by density modulations."
In Shapiro, A. G., and Todorovic, D. (eds.), \emph{Oxford Compendium of Visual Illusions}, Oxford University Press, Oxford.\\

\years{2008}
Hamoud, R. I. and Mulligan, J. B., (2008).
``Introduction to Eye Monitoring."
In Hamoud, R. I. (ed.), \emph{Passive Eye Monitoring},
Springer-Verlag, Berlin.


\subsection*{NASA Technical Memoranda}
\noindent

\years{1989}
Stone, L. S., Watson, A. B., and Mulligan, J. B., (1989).
\emph{Effect of contrast on the perception of direction of a moving pattern.}
NASA Tech. Memo. \#102234.\\

\years{1988}
Mulligan, J. B., and Stone, L. S., (1988),
\emph{Efficient use of bit planes in the generation of motion stimuli.}
NASA Tech. Memo. \#101022.\\

%\clearpage
\clearpage
\section*{Invited presentations}

\years{2018}
``An architecture of visual processing revealed by eye movements."
Smith-Kettlewell Eye Research Institute, San Francisco.\\

\years{2017}
``Color algebras."  Dept. of Psychology, University of Nevada at Reno.\\

\years{2015}
``Measuring and modeling shared visual attention."
Dept. of Cognitive Sciences, University of California at Irvine.\\

``An architecture of visual processing revealed by eye movements."
Center for Visual Science, University of Rochester.\\

\years{2013}
``Taking gaze tracking from the laboratory to the field (and sky)."
Project Glass group, Google Research, Mountain View, CA.\\

\years{2012}
``An eye movement-defined hierarchy of visual stimuli."  CMU West, Moffett Field CA.\\

\years{2011}
``An eye movement-defined hierarchy of visual stimuli."  City University of London, U.K.\\

\years{2010}
``Visual dynamics revealed by oculomotor oscillations."  Center for Perceptual Systems, University of Texas at Austin.\\

``Visual dynamics revealed by oculomotor oscillations."  Dept. of Psychology, University of California at Santa Cruz.\\

\years{2008}
``Visual dynamics revealed by oculomotor oscillations."  Dept. of Psychology, University of California at Los Angeles.\\

%\clearpage
\years{2007}
``Spontaneous oculomotor oscillations induced by delayed visual feedback."  Giessen University, Germany.\\

``Spontaneous oculomotor oscillations induced by delayed visual feedback."  University of Padova, Italy.\\

``Spontaneous oculomotor oscillations induced by delayed visual feedback."  University of California at Irvine.\\

\years{2005}
``Inference of cognitive state from gaze behaviors ."  Symposium on Bio-inspired Processing, Luebeck, Germany.\\

``Inference of cognitive state from gaze behaviors ."  Dept. of Computer Science, University of Bremen, Bremen, Germany.\\

``Biometric applications of active illumination."  Agilent Laboratories, Palo Alto CA.\\

``Taking gaze tracking from the laboratory to the field (and sky)."  Intel Laboratories, Santa Clara CA.\\

``Taking gaze tracking from the laboratory to the field (and sky)."  Dept. of Psychology, University of Nevada at Reno.\\

\years{2003}
``The eye movement correlogram:  a new physiological tool for probing the time course of visual processing."  UC Berkeley School of Optometry, Berkeley CA.\\

\years{2002}
``Vision-based approaches to digital halftoning."  PICS Conference, Portland OR.\\

``A model of visual tracking suggests a biphasic motion response."  University of Houston College of Optometry, Houston TX.\\

\years{1993}
``Improving digital halftones by exploiting visual system properties."
27th Asilomar conference on Signals, Systems and Computers.

\clearpage
\section*{Presentations}

\subsection*{Conference presentations with published abstracts}
\noindent

%\hrulefill

\years{2018}
Mulligan, J. B. (in press).
``Discovery of activities via statistical clustering of fixation patterns."
\emph{J. Vis.}, (Vision Sciences Society annual meeting abstracts).\\

\years{2017}
Mulligan, J. B., Diaz-Piedra, C., and di Stasi, L. L. (2017).
``Oculomotor assessment of diurnal arousal variations."
\emph{J. Vis.}, v. 17(10), p. 1153.\\

Mulligan, J. B., and Kalar, D. J. (2017).
``Identification of fixations in noisy eye movement data via recursive subdivision."
\emph{J. Vis.}, v. 17(7), p. 43.\\

\years{2016}
Stevenson, S., Mahadevan, M., and Mulligan, J. (2016).
``Attentional modulation of eye torsion responses."
\emph{J. Vis.}, v. 16(12), p. 1304.\\

Mulligan, J. B., and Gontar, P. (2016).
``Measuring and modeling shared visual attention."
Proc. 5th annual workshop on Computational and Mathematical Models in Vision (MODVIS). 
\href{http://docs.lib.purdue.edu/cgi/viewcontent.cgi?article=1058&context=modvis}{PDF}\\

Mulligan, J. B., Arsintescu, L., and Flynn-Evans, E. E. (2016).
``Measurement of visual reaction times using hand-held mobile devices."
\emph{J. Vis.}, v. 16(4), p. 41.\\

\years{2015}
Mulligan, J. B. (2015).
``Psychophysical calibration of mobile touch screens for vision testing in the field."
\emph{J. Vis.}, v. 15(12), p. 475.\\

\years{2014}
Mulligan, J. B., and Stevenson, S. B. (2014).
``Smooth pursuit of flicker-defined motion."
\emph{J. Vis.}, v. 14(10), p. 493.\\

\years{2013}
Mulligan, J. B. (2013).
``Rapid Assessment of Contrast Sensitivity with Mobile Touch-screens."
\emph{J. Vis.}, v. 13(9), p. 270.\\

Mulligan, J. B. (2013).
``Visual nonlinearities and the perception of shimmer in repetetive patterns."
\emph{J. Vis.}, v. 13(15), p. P16.\\

\years{2012}
Mulligan, J. B. (2012).
``The phantom spokes illusion."
\emph{J. Vis.}, v. 12(9), p. 1211.\\

Mulligan, J. B., and Stevenson, S. B. (2012).
``An Eye-Movement-Defined Hierarchy of Visual Stimuli."
\emph{J. Vis.}, v. 11(15), p. 52.\\

\years{2011}
Mulligan, J. B. (2011).
``Assessing visual delays using pupil oscillations."
\emph{J. Vis.}, v. 11(11), p. 504.\\

%\vspace{10 mm}

\years{2010}
Mulligan, J. B., and Steelman-Allen, K. S. (2010).
``Conspicuity of peripheral visual alerts."
\emph{J. Vis.}, v. 10(7), p. 150.\\

McDermott, K. C., Malkoc, G., Mulligan, J. B., and Webster, M. A. (2010).
``Adaptation and visual salience."
\emph{J. Vis.}, v. 10(13), p. 17.\\

Mulligan, J. B. (2010).
``Factors influencing scanning for alerts."
\emph{J. Vis.}, v. 10(15), p. 69.\\

\years{2009}
Mulligan, J. B., and Stevenson, S. B. (2009).
``No role for visual motion in manual tracking."
\emph{J. Vis.}, v. 9(14), p. 67.\\

Mulligan, J. B., and Stevenson, S. B. (2009).
``A comparison of the dynamics of visually-controlled head and hand movements."
\emph{J. Vis.}, v. 9(8), p. 846.\\

\years{2008}
Mulligan, J. B., and Stevenson, S. B. (2008).
``A frequency sweep method for rapid estimation of visual delays."
\emph{J. Vis.}, v. 8(6), p. 366.\\

%\clearpage
\years{2007}
Mulligan, J. B., and Stevenson, S. B. (2007).
``Spontaneous vergence oscillations induced by delayed visual feedback."
\emph{J. Eye Movement Res.}, v. 1(1), p. 40.\\

Mulligan, J. B., and Stevenson, S. B. (2007).
``Pursuit response to tritanopic stimuli."
\emph{Perception}, v. 36, ECVP Abstract Supplement, p. 166.\\

Mulligan, J. B., and Stevenson, S. B. (2007).
``Spontaneous oculomotor oscillations induced by delayed visual feedback."
\emph{J. Vis.}, v. 7(9), p. 320.\\

\years{2006}
McDermott, K. C., Mulligan, J. B., Bebis, G., and Webster, M. A. (2006).
``Visual search in familiar contexts – effects of learning or adaptation?"
\emph{J. Vis.}, v. 6(6), p. 527.\\

Mulligan, J. B., and Trujillo, M. T. (2006).
``Temporal summation in trajectory perception."
\emph{J. Vis.}, 6(6), p. 1082.\\

\years{2005}
Mulligan, J. B. (2005).
``Optical eye models for gaze tracking."
\emph{J. Vis.}, 5(12), p. 77.\\

McDermott, K., Loving, R., Mulligan, J. B., Bebis, G., and Webster, M. A. (2005).
``Eye movements and visual search in novel and familiar contexts."
\emph{J. Vis.}, 5(12), p. 73.\\

\clearpage
Mulligan, J. B., Stevenson, S. B., and Cormack, L. K., (2005).
``The effect of plaid orientation on pursuit of partially-predictable motion."
\emph{J. Vis.}, 5(8), article 440
Proc. Vision Sciences Society 5th Annual Meeting, p. 122.\\

\years{2004}
Mulligan, J. B. (2004).
``Taking gaze tracking from the lab to the field (and sky)."
\emph{J. Vis.}, 4(11), p. 13.\\

Mulligan, J. B., Stevenson, S. B., and Cormack, L. K., (2004).
``Polarization analysis of the eye movement correlogram."
\emph{J. Vis.}, 4(8), article 651
(Proc. Vision Sciences Society 4th Annual Meeting, p. 168).\\

Snyder, J. L., Mulligan, J. B., and Maloney, L. T., (2004).
``Horizontal binocular disparity facilitates visual search
in stereoscopically-viewed displays."
\emph{J. Vis.}, 4(8), article 679
(Proc. Vision Sciences Society 4th Annual Meeting)\\

\years{2003}
Yang, J., and Mulligan, J. B., (2003).
``Readability of chromatic transparent text on a patterned background."
\emph{J. Vis.}, 3(9), article 448
(Proc. Vision Sciences Society 3rd Annual Meeting, p. 128).\\

%\clearpage
Stevenson, S. B., Mulligan, J. B., and Cormack, L. K., (2003).
``Attention adds a long latency component in eye movement correlograms."
\emph{J. Vis.}, 3(9), article 143
(Proc. Vision Sciences Society 3rd Annual Meeting, p. 47).\\

Mulligan, J. B., and Stevenson, S. B., (2003).
``The contrast dependence of eye-movement latencies."
\emph{J. Vis.}, 3(9), article 438
(Proc. Vision Sciences Society 3rd Annual Meeting, p. 125-126).\\

Mulligan, J. B., (2003).
``Anisotropy in the eye movement correlogram."
\emph{Perception},
v.  32 (ECVP supplement), p. 23.\\

\years{2002}
Mulligan, J. B. and Stevenson, S. B. (2002).
``Speed-dependent delays for smooth eye movements."
\emph{J. Vis.}, 2(10), p. 20.\\

Mulligan, J. B. (2002).
``A model of oculomotor tracking suggests a biphasic motion response."
\emph{J. Vis.}, v. 2(7)
(Proc. Vision Sciences Society 2nd Annual Meeting, p. 199).\\

\years{2001}
Mulligan, J. B., and Huemer, V. A., (2001).
``Effects of color-coding on search in air traffic displays assessed by scan-path analysis."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v.  42, p. 927.\\

Mulligan, J. B., (2001).
``Sensory processing delays measured with the eye-movement correlogram."
\emph{Optics Express}, v.  9, p. 12.
(Optical Society of America, Vision and Color Meeting)\\

%\clearpage
\years{2000}
Mulligan, J. B., (2000).
``Scan path analysis of air traffic control displays."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v.  41, p. 423.\\

\years{1999}
Mulligan, J. B., and Grosof, D. H., (1999).
``What the pilot's brain tells the pilot's eye."
\emph{OSA 1999 Annual Meeting}.\\

Mulligan, J. B., (1999).
``Eye tracking using multiple features."
\emph{OSA 1999 Annual Meeting}.\\

Watson, A. B., Hu, Q. J., McGowan, J. F., and Mulligan, J. B. (1999).
``Design and performance of a digital video quality metric."
in Rogowitz, B. E., and Pappas, T. N. (eds.),
\emph{Human Vision and Electronic Imaging IV},
Proc. SPIE, v. 3644.\\

\years{1998}
Mulligan, J. B., (1998).
``Video-based head and eye tracking."
\emph{OSA 1998 Annual Meeting}.\\

Mulligan, J. B., (1998).
``Pursuit latency for chromatic targets."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 39, p. S444.\\

Grosof, D. H., Mulligan, J. B., and Gidday, J. M. (1998).
``Improved Estimates of CNS Blood Flow by Image Registration of Angiographic Videos."
\emph{Soc. Neurosci. Abs.}, v. 24, p. 429.\\

\years{1997}
Mulligan, J. B., (1997).
``Image rotation does not rotate smooth eye movements."
\emph{OSA 1996 Annual Meeting}.\\

Mulligan, J. B., (1997).
``Eye movements reveal hierarchical motion processing."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 38, p. S937.\\

\years{1996}
Mulligan, J. B., (1996).
``Eye-movement tracking using fundus images."
\emph{OSA 1996 Annual Meeting}, p. 82.\\

Mulligan, J. B., (1996).
``Perception and pursuit of velocity perturbations."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 37, p. 432.\\

\years{1995}
Mulligan J. B., Beutter, B. R., and Stevenson, S. B., (1995).
``Reflexive OKN is biased like perception."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 36, p. 205.\\

\clearpage
Mulligan, J. B., (1995).
``Temporal MTF of motion perception."
\emph{OSA 1995 Annual Meeting}, p. 148.\\

%\clearpage
Beutter, B. R., Mulligan, J. B., and Stone, L. S., (1995).
``Analysis of the trial-by-trial correlation between eye movement and perceptual responses to moving plaids."
\emph{Soc. Neurosci. Abs.}, v. 21, p. 141.\\

\years{1994}
Mulligan, J. B., and Beutter, B. R., (1994).
``Additional twists on a continuous barber pole illusion."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 35, p. 2158.\\

Beutter, B. R., and Mulligan, J. B., (1994).
``The barberplaid illusion."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 35, p. 2157.\\

Beutter, B. R., Mulligan, J. B., and Stone, L. S., (1994).
``Direction of moving plaids is biased by asymmetric viewing windows."
\emph{Soc. Neurosci. Abs.},
v. 20, p. 772.\\

\years{1993}
Mulligan, J. B., (1993).
``Classification of Color X-Junctions."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 34, p. 766.\\

%\clearpage
\years{1992}
Mulligan, J. B., (1992).
``Motion transparency is restricted to two planes."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 33, p. 1049.\\

Mulligan, J. B., (1992).
``Symmetric models of color constancy."
\emph{OSA Annual Meeting Technical Digest}, v. 23, p. 62.\\

\years{1991}
Mulligan, J. B., (1991).
``A continuous version of the barber-pole illusion."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 32, p. 829.\\

Shiffrar, M., and Mulligan, J. B., (1991).
``A test for models of motion processing:  nonrigidly perceived rotating ellipses."
\emph{32nd annual meeting of the Psychonomic Society}, p. 30.\\

Mulligan, J. B., and Shiffrar, M., (1991).
``Perception of rigidity with rotating ellipses."
\emph{OSA Annual Meeting Technical Digest}, v. 17, p. 225.\\

\years{1990}
Mulligan, J. B., (1990).
``Channel model of motion transparency."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 31, p. 528.\\

Ahumada, A. J., Jr., and Mulligan, J. B., (1990).
``Learning networks for the red-green opponent system."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 31, p. 262.\\

\clearpage
Mulligan, J. B., (1990).
``Linear model of color transparency."
\emph{Optical Society of America Annual Meeting Technical Digest},
p. 268.\\

%\clearpage
\years{1989}
Mulligan, J. B., and Cunningham, H. A., (1989).
``Motion capture unmasked."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 30, p. 388.\\

\years{1988}
Stone, L. S., Mulligan, J. B., and Watson, A. B., (1988).
``Neural determination of the direction of motion:  contrast affects the perceived direction of a moving plaid."
\emph{Soc. Neurosci. Abs.},
v. 14, p. 1251.\\

Stone, L. S., Mulligan, J. B., and Watson, A. B., (1988).
``Contrast affects the perceived direction of a moving plaid."
\emph{Optics News},  v. 14 no. 9, p. 206.\\

Mulligan, J. B., (1988).
``Factors affecting the perception of transparent motion."
\emph{Optics News},  v. 14 no. 9, p. 206.\\

Mulligan, J. B., (1988).
``Perceived position depends on velocity."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 29, p. 251.\\

%\clearpage
\years{1987}
Mulligan, J. B., (1987).
``A simple method for colorimetric calibration of color TV displays."
\emph{Optics News},  v. 13, no. 9, p. 166.\\

\years{1986}
Mulligan, J. B., (1986), "Algorithms for computing structure-from-motion
evaluated using an ambiguous kinetic depth effect."
\emph{Inv. Ophth. Vis. Sci.}
(suppl.), v. 27, p. 142.\\

Chen, B., MacLeod, D. I. A., and Mulligan, J. B., (1986).
``Does the inhibitory surround improve resolution under light adapted conditions?"
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 27, p. 344.\\

\years{1985}
Mulligan J. B., (1985).
``Chromatic modulation sensitivity unimpaired by sampling."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 26, p. 206.\\

\years{1984}
Mulligan J. B. and MacLeod D. I. A., (1984).
``Pooling of perceived brightness among distinct texture elements."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 25, p. 199.\\

\years{1983}
Mulligan J. B. and Krauskopf J., (1983).
``Vernier acuity for chromatic stimuli."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 24, p. 276.\\

MacLeod D. I. A., Nakayama K., Silverman G. and Mulligan J. B., (1983).
``Anisotropic spatial integration in the detection of movement."
\emph{Inv. Ophth. Vis. Sci.} (suppl.), v. 24, p. 277.\\

%\clearpage
\years{1982}
Nakayama K., Silverman G., Mulligan J., and MacLeod D. I. A., (1982).
``Anisotropic spatial integration in motion detection."
\emph{Fifth European Conference on Visual Perception}, Groot Begijnhof, Leuven, Belgium, September 1982.\\

Mulligan J. B., (1982).
``Binocular mechanisms in the processing of moving textures."
\emph{Inv. Ophth. Vis. Sci.}
(suppl.), v. 22, p. 145.

\noindent

\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
%\fontspec{Times New Roman}
\XeTeX } 
% put the two backslashes after the brace above if the cv pdf URL will follow...
%\\
% and then get rid of this brace...
}
% ---- FILL IN THE FULL URL TO YOUR CV HERE
%\href{http://scanpath.arc.nasa.gov/jbm/jbm\_cv.pdf}
%{http://scanpath.arc.nasa.gov/jbm\_cv.pdf}
%}
\end{center}

\end{document}
