%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

%\documentclass[12pt, a4paper]{article}
\documentclass[12pt]{article}
\usepackage{fontspec} 

% DOCUMENT LAYOUT
\usepackage{geometry} 
%\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\geometry{textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Jeffrey Mulligan - vita},
	pdfauthor={Jeff Mulligan},
	pdfproducer={http://nitens.org/taraborelli/cvtex}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

% DOCUMENT
\begin{document}
{\LARGE Jeffrey Brooke Mulligan}\\[1cm]
 Human Systems Integration Division\\
 NASA Ames Research Center\\
MS 262-2\\
Moffett Field, CA \texttt{94035}
\\[.2cm]
Phone: \texttt{650-604-3745}\\
Fax: \texttt{650-604-3323}\\[.2cm]
email: \href{mailto:jeffrey.b.mulligan@nasa.gov}{jeffrey.b.mulligan@nasa.gov}\\
\textsc{url}: \href{http://hsi.arc.nasa.gov/groups/scanpath/}{http://hsi.arc.nasa.gov/groups/scanpath/}\\ 
alt. email: \href{mailto:jbmull@gmail.com}{jbmull@gmail.com}\\
%\vfill
% Born:  December 14, 1958---Detroit, MI\\

%%\hrule
%\section*{Current position}
%%\emph{Emeritus Professor}, Institute for Advanced Study, Princeton
%Computer Engineer (GS 14-10), NASA Ames Research Center

%%%\hrule
%\section*{Skills}
% Psychophysical research • Optics • Electronic design • Computer programming

%\hrule
\section*{Education}
\noindent
\years{1986}\textsc{PhD} in Psychology, University of California at San Diego\\
\years{1982}\textsc{MA} in Psychology, University of California at San Diego\\
\years{1980}\textsc{AB} in Physics (\emph{cum laude} general studies), Harvard University\\
\years{1975}US Math Olympiad Summer Program, Rutgers University\\

%%\hrule
\section*{Employment}
\noindent
\years{1987-present}Computer engineer, NASA Ames Research Center\\
\years{1986-1987}National Research Council post-doctoral associate, NASA Ames Research Center\\
\years{1980-1986}Research and teaching assistant, Department of Psychology, UC San Diego\\
\years{1982-1983}Research assistant, AT\&T Bell Laboratories, Murray Hill NJ\\
\years{1980}Research assistant, Division of Applied Sciences, Harvard University\\

\section*{Teaching}
\noindent
\years{1991}Introduction to Computer Science, UC Santa Cruz\\
\years{1991}Data Structures, UC Santa Cruz\\
\years{1990}Sensation \& Perception, Cal. State Hayward (Contra Costa campus)\\
\years{1980-1986}Teaching assistant, Department of Psychology, UC San Diego\\
courses taught:  sensory laboratory, neuropsychology

%\hrule
\section*{Professional societies}
\noindent
\years{2001-present}Vision Sciences Society (VSS)\\
\years{1984-present}Optical Society of America (OSA)\\
\years{2005-present}Society for Information Display (SID)\\
\years{1982-2001}Association for Research in Vision and Ophthalmology (ARVO)\\

%\hrule
\section*{Professional service}
\subsection*{Conference organization}
\noindent
\years{2015}Chair, local organizing committee, OSA Fall Vision Meeting\\
\years{2013-2016}Chair/Vice-chair, Vision technical committee, Vision and Color division,  OSA\\
%\years{2010-2013}Vice-chair, Vision technical committee, Vision and Color division,  OSA\\
\years{2012-present}Co-organizer, VSS satellite workshop on\\
\hspace*{5 mm}Computational and Mathematical Models in Vision (MODVIS)\\
\years{2011-2014}Program co-chair, ACM Symposium on Eye Tracking Research and Applications\\
\years{2009-2010}Area chair, ACM Symposium on Eye Tracking Research and Applications\\
\years{2004-present}Program committee, SPIE/IS\&T Conference on\\
\hspace*{5 mm}Human Vision and Electronic Imaging\\
\years{2005-present}Program committee (Applied Vision subcommittee)\\
\hspace*{5 mm}Society for Information Display\\
\years{2006-present}Program committee, International Symposium on Visual Computing\\

\subsection*{Standards committees}
\years{2013-present}COGAIN technical committee for eye tracker data quality standardization\\
\years{2016-present}ICDM - International Committee for Display Metrology\\

\subsection*{\emph{Ad hoc} reviewing}
Journal of Vision (``exceptional reviewer")\\
Vision Research\\
Journal of the Optical Society of America, A\\
Displays\\
Biomedical Optics Express\\
IEEE Transactions on Biomedical Engineering\\
Physiological Measurement\\
Optics Letters\\
Journal of Aircraft\\

%\hrule
\section*{Honors \& awards}
\noindent
\years{2009}NASA group achievement award, Constellation Training Facility team\\
\years{1983-1985}IBM graduate fellowship\\
\years{1984}NIH travel scholarship to attend International School of Biophysics (Italy)\\
\years{1983}ARVO travel fellowship\\


%\vspace{10 mm}

%\clearpage
\section*{Software}
\years{2009,2016}
QuIP - An interactive environment for QUick Image Processing.  The QuIP interpreter provides a convenient interface to libraries for image processing, graphics, image acquisition, and control of other pieces of laboratory hardware.  The systems runs on unix-like systems (linux, Mac OSX), and Apple iOS.  GPU acceleration is provided with either CUDA or OpenCL.\\
\href{https://github.com/nasa/QuIP}{https://github.com/nasa/QuIP}

\section*{Publications}


\subsection*{Journal articles (17) \& proceedings papers (32)}
\noindent

\years{2018}
Mulligan, J. B. (2018).  ``Statistical identifications of fixations in noisy eye movement data." in Rogowitz, B. E. Pappas, T. N., and de Ridder, H. (eds.), \emph{Human Vision and Electronic Imaging 2018, IS\&T International Symposium on Electronic Imaging 2018}.\\

\years{2017}
Arsintescu, L., Mulligan, J. B., and Flynn-Evans, E. E. (2017).
``Evaluation of psychomotor vigilance task for touch screen devices."
\emph{Human Factors},
\newline
DOI:10.1177/0018720816688394.
\href{https://hsi.arc.nasa.gov/publications/Arsintescu_Mulligan_Flynn-Evans_pvt.pdf}{PDF}
\\

\years{2016}
Mulligan, J. B. (2016).  ``A method for rapid measurement of contrast sensitivity on mobile touch-screens." in Rogowitz, B. E. Pappas, T. N., and de Ridder, H. (eds.), \emph{Human Vision and Electronic Imaging 2016, IS\&T International Symposium on Electronic Imaging 2016},  pp. HVEI-104.1 - HVEI-104.6.  \href{http://www.ingentaconnect.com/contentone/ist/ei/2016/00002016/00000016/art00009}{PDF}\\

\years{2013}
Mulligan, J. B., Stevenson, S. B., and Cormack, L. K. (2013).
``Reflexive and voluntary control of smooth eye movements.”
in Rogowitz, B. E. Pappas, T. N., and de Ridder, H. (eds.),
\emph{Human Vision and Electronic Imaging XVIII},
Proc. SPIE, v. 8651.  \href{http://scanpath.arc.nasa.gov/pub_files/spie13.pdf}{PDF}\\

\years{2012}
Mulligan, J. B. (2012).
``A GPU-accelerated software eye tracking system.”
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA),
pp. 265-268.  \href{http://scanpath.arc.nasa.gov/pub_files/etra12.pdf}{PDF}\\

\years{2010}
Mulligan, J. B., and Gabayan, K. N. (2010).
``Robust optical eye detection during head movement.”
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA),
pp. 129-132.  \href{http://scanpath.arc.nasa.gov/pub_files/etra10.pdf}{PDF}\\

McDermott, K. C., Malkoc, G., Mulligan, J. B., and Webster, M. A. (2010).
``Adaptation and visual salience."
\emph{J. Vis.}, v. 10(13), pp. 1-32.\\

\years{2009}
Mulligan, J. B. (2009).
``Presentation of calibrated images on the web.”
in Rogowitz, B. E. and Pappas, T. N. (eds.),
\emph{Human Vision and Electronic Imaging XIV},
Proc. SPIE, v. 7240.  \href{http://scanpath.arc.nasa.gov/pub_files/spie09.pdf}{PDF}\\

Ahumada, A. J., Jr., Kaiser, M. K., and Mulligan, J. B. (2009).
``The dynamic range of visual imagery in space.”
in Rogowitz, B. E. and Pappas, T. N. (eds.),
\emph{Human Vision and Electronic Imaging XIV},
Proc. SPIE, v. 7240.\\

Mulligan, J. B. (2009)
``Motion parallax enhances depth in a perspective air-traffic display."
\emph{SID Symposium Digest of Technical Papers}, v. 40(1), pp. 1231-1233.  \href{http://scanpath.arc.nasa.gov/pub_files/sid09.pdf}{PDF}\\

\years{2008}
Mulligan, J. B. (2008).
``Measurement of eye velocity using active illumination.”
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA),
pp. 35-38.  \href{http://scanpath.arc.nasa.gov/pub_files/etra08.pdf}{PDF}\\

\years{2006}
Mulligan, J. B. (2006).
``Optical eye models for gaze tracking.”
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA), p. 51.  \href{http://scanpath.arc.nasa.gov/pub_files/etra06.pdf}{PDF}\\

McDermott, K., Mulligan, J. B., Bebis, G., and Webster, M. A. (2006).
``Visual search and eye movements in novel and familiar contexts.”
in Rogowitz, B. E., Pappas, T. N., and Daly, S. J. (eds.),
\emph{Human Vision and Electronic Imaging XI},
Proc. SPIE, v. 6057.\\

\years{2005}
Mulligan, J. B. (2005).
``A tree-structured model of visual appearance applied to gaze-tracking."
In Bebis, G., Boyle, R., Koracin, D., and Parvin, B. (eds.),
\emph{First International Symposium on Visual Computing},
Springer Lecture Notes on Computer Science v. 3804, pp. 303-312.  \href{http://scanpath.arc.nasa.gov/pub_files/isvc05.pdf}{PDF}\\

Mulligan, J. B., and Brolly, X. L. C. (2005).
``Pilot behavior and course deviations during precision flight.”
in Rogowitz, B. E. and Pappas, T. N. (eds.),
\emph{Human Vision and Electronic Imaging X},
Proc. SPIE, v. 5666,
pp. 362-373.  \href{http://scanpath.arc.nasa.gov/pub_files/spie05.pdf}{PDF}\\
% Human Vision and Electronic Imaging X, pp.  362-373.

\years{2004}
Mulligan, J. B., and Brolly, X. L. C. (2004).
``Surface determination by photometric ranging."
\emph{Conference on Computer Vision and Pattern Recognition Workshop} (CVPRW04),
v. 3, pp. 40-47.  \href{http://scanpath.arc.nasa.gov/pub_files/ranging.pdf}{PDF}\\

Brolly, X. L. C., and Mulligan, J. B. (2004).
``Implicit calibration of a remote gaze tracker."
\emph{Conference on Computer Vision and Pattern Recognition Workshop} (CVPRW04),
v. 8, pp. 134-141.  \href{http://scanpath.arc.nasa.gov/pub_files/galvo.pdf}{PDF}\\

% clearpage forces a page break - we do this so citations
% don't straddle page breaks - but these have to be placed by hand!?
\clearpage
Meyer, G. F., Mulligan, J. B., and Wuerger, S. M. (2004).
``Continuous audio-visual digit recognition using N-best decision fusion."
\emph{Information Fusion}, v. 5(2), pp. 91-101.\\

\years{2003}
Brolly, X. L. C., Stratelos, C., and Mulligan, J. B. (2003).
``Model-based head pose estimation for air-traffic controllers."
\emph{Proc. IEEE International Conf. on Image Processing} (ICIP),
Barcelona, Spain, v. 3, pp 113-116.  \href{http://scanpath.arc.nasa.gov/pub_files/icip03.pdf}{PDF}\\

\years{2002}
Mulligan, J. B., (2002).
``A software-based eye tracking system for the study of air-traffic displays."
\emph{Proc. ACM Symposium on Eye Tracking Research and Applications} (ETRA),
pp. 69-76.  \href{http://scanpath.arc.nasa.gov/pub_files/etra02jbm.pdf}{PDF}\\

Mulligan, J. B., (2002).
``Vision-based approaches to digital halftoning."
\emph{Proc. 55th Annual Conference
of the Society for Imaging Science and Technology},
Portland OR, pp. 1-4.  \href{http://scanpath.arc.nasa.gov/pub_files/pics02_jbm.pdf}{PDF}\\

\years{2001}
Mulligan, J. B., (2001).
``Sensory processing delays measured with the eye movement correlogram."
in Kaminski, H. J., and Leigh, R. J. (eds.),
``Neurobiology of eye movements:  from molecules to behavior."
\emph{Annals of the New York Academy of Science}, v. 956, pp. 476-478.\\

\years{1999}
Watson, A. B., Hu, Q. J., McGowan, J. F. III, and Mulligan, J. B., (1999).
``Design and performance of a digital video quality metric."
\emph{Human Vision and Electronic Imaging IV}, 
Proc. SPIE, v. 3644,
pp. 168-174.\\

\years{1997}
Mulligan, J. B., (1997).
``Application of Motion-JPEG to dynamic stimulus presentation."
\emph{Spatial Vision}, v. 11, pp. 19-32.  \href{http://scanpath.arc.nasa.gov/pub_files/mjpeg.pdf}{PDF}\\

Mulligan, J. B., (1997).
``Image processing for improved eye tracking accuracy."
\emph{Behavior Research Methods, Instrumentation and Computers},
v. 29, pp. 54-65.  \href{http://scanpath.arc.nasa.gov/pub_files/mulligan_brmic97.pdf}{PDF}\\

Mulligan, J. B., (1997).
``Application of temporal error diffusion to motion JPEG."
in Rogowitz, B. E. and Pappas, T. N. (eds.),
\emph{Human Vision and Electronic Imaging II},
Proc. SPIE, v. 3016,
pp. 288-295.\\

Mulligan, J. B., (1997).
``Recovery of motion parameters from distortions in scanned images."
in Le Moigne, J. (ed.),
\emph{Proc. Image Registration Workshop},
NASA Goddard Space Flight Center, Greenbelt, Maryland, November 20-21, 1997.
NASA Publication \# CP-1998-206853.  \href{http://scanpath.arc.nasa.gov/pub_files/irw97.pdf}{PDF}\\

\years{1996}
Beutter, B. R., Mulligan, J. B., and Stone, L. S., (1996).
``The barberplaid illusion:  plaid motion is biased by elongated apertures."
\emph{Vision Res.}, v. 36, pp. 3061-3075.\\

Mulligan, J. B., (1996).
``When are supercomputers worth the bother?"
\emph{Behavior Research Methods, Instrumentation and Computers},
v. 28, pp. 239-240.\\

\years{1995}
Mulligan, J. B., and Beutter, B. R., (1995).
``Eye-movement tracking using compressed video images."
\emph{Vision Science and its Applications},
1995 Technical Digest Series,
v. 1,
Optical Society of America,
pp. 163-166.\\

\years{1994}
Mulligan, J. B., and MacLeod, D. I. A., (1994).
``In search of an optoretinogram."
\emph{Vision Science and its Applications},
1994 Technical Digest Series,
v. 2,
Optical Society of America,
pp. 167-170.\\

\years{1993}
Mulligan, J. B., (1993).
``Nonlinear combination rules and the perception of motion transparency."
\emph{Vision Res.},
v. 33, pp. 2021-2030.  \href{http://scanpath.arc.nasa.gov/pub_files/vr93.pdf}{PDF}\\

%\clearpage
Mulligan, J. B., (1993).
``Methods for spatiotemporal dithering."
\emph{SID International Symposium Digest of Technical Papers},
v. 24, pp. 155-158.\\

Mulligan, J. B., (1993).
``Improving digital halftones by exploiting visual system properties."
in Singh, A. (ed.), Conference record,
\emph{27th Asilomar conference on Signals, Systems and Computers},
IEEE Computer Society Press,
pp. 961-965.  \href{http://scanpath.arc.nasa.gov/pub_files/asil93.pdf}{PDF}\\

\years{1992}
Mulligan, J. B., (1992).
``Anisotropy in an ambiguous kinetic depth effect."
\emph{J. Opt. Soc. Am. A},
v. 9, pp. 521-529.  \href{http://scanpath.arc.nasa.gov/pub_files/josa92.pdf}{PDF}\\

Mulligan, J. B., and Ahumada, A. J., Jr., (1992).
``Principled halftoning based on human vision models."
in Rogowitz, B. E. (ed.),
\emph{Human Vision, Visual Processing, and Visual Display III},
Proc. SPIE, v. 1666,
pp. 109-121.  \href{http://scanpath.arc.nasa.gov/pub_files/spie92.pdf}{PDF}\\

Mulligan, J. B., and Ahumada, A. J. Jr., (1992).
``Principled methods for color dithering based on models of the human visual system."
\emph{SID International Symposium Digest of Technical Papers},
v. 23, pp. 194-197.\\

\years{1991}
Mulligan, J. B. and MacLeod, D. I. A., (1991).
``Visual sensitivity to spatially sampled modulation in human observers."
\emph{Vision Res.}, v. 31, pp. 895-905.  \href{http://scanpath.arc.nasa.gov/pub_files/vr91.pdf}{PDF}\\

Ahumada, A. J., Jr., and Mulligan, J. B., (1991).
``Network compensation for missing sensors."
in Rogowitz, B. E., Brill, M. H., and Allebach, J. P. (eds.),
\emph{Human Vision, Visual Processing, and Visual Display II},
Proc. SPIE, v. 1453,
pp. 134-146.\\

\years{1990}
Stone, L. S., Watson, A. B., and Mulligan, J. B., (1990).
``Effect of contrast on the perceived direction of a moving plaid."
\emph{Vision Res}., v. 30, pp. 1049-1067.\\

Ahumada, A. J., Jr., and Mulligan, J. B., (1990).
``Learning receptor positions from imperfectly known motions."
in Rogowitz, B. E., and Allebach, J. P. (eds.),
\emph{Human Vision and Electronic Imaging:  Models, Methods, and Applications},
Proc. SPIE, v. 1249,
pp. 124-134.\\

Mulligan, J. B., (1990).
``Digital halftoning methods for selectively partitioning
error into achromatic and chromatic channels."
in Rogowitz, B. E., and Allebach, J. P. (eds.),
\emph{Human Vision and Electronic Imaging:  Models, Methods, and Applications},
Proc. SPIE, v. 1249,
pp. 261-270.  \href{http://scanpath.arc.nasa.gov/pub_files/spie90.pdf}{PDF}\\

\years{1989}
Mulligan, J. B., and Stone, L. S., (1989).
``Halftoning method for the generation of motion stimuli."
\emph{J. Opt. Soc. Am.}, v. 6, pp. 1217-1227.  \href{http://scanpath.arc.nasa.gov/pub_files/josa89.pdf}{PDF}\\

%\clearpage
Ahumada, A. J., Jr., and Mulligan, J. B., (1989).
``Learning in interpolation networks for irregular sampling: some convergence properties."
\emph{OSA Topical Meeting on Applied Vision},
1989 Technical Digest Series,  v. 16, pp. WC3-1 - WC3-4.\\

\years{1988}
Mulligan, J. B., and MacLeod, D. I. A., (1988).
``Reciprocity between luminance and dot density in the perception of brightness."
\emph{Vision Res}., v. 28, 503-519.  \href{http://scanpath.arc.nasa.gov/pub_files/vr88.pdf}{PDF}\\

\years{1986}
Mulligan J. B., (1986).
``Optimizing stereo separation in color television anaglyphs."
\emph{Perception}, v. 15, pp. 27-36.\\

Mulligan J. B., (1986).
``Minimizing quantization errors in a digitally controlled CRT."
\emph{Color Res. Appl.} (suppl.), v. 11, pp. S47-S51.\\

\years{1985}
Nakayama K., Silverman G., MacLeod D. I. A., and Mulligan J. B., (1985).
``Sensitivity to shearing and compressive motion in random dots."
\emph{Perception}, v. 14, pp. 225-238.\\

\years{1982}
Stromeyer C. F. III, Mulligan J. B., Birch D. G., and Dawson B. M., (1982).
``Adaptation to polarized light in humans."
\emph{Vision Res.}, v. 22, pp. 217-224.\\

\clearpage

\subsection*{Book Chapters}
\noindent

\years{2016}  Mulligan, J. B. (in press).  ``Illusory variations in apparent dot brightness induced by density modulations."
In Shapiro, A. G., and Todorovic, D. (eds.), \emph{Oxford Compendium of Visual Illusions}, Oxford University Press, Oxford.\\

\years{2008}
Hamoud, R. I. and Mulligan, J. B., (2008).
``Introduction to Eye Monitoring."
In Hamoud, R. I. (ed.), \emph{Passive Eye Monitoring},
Springer-Verlag, Berlin.


\subsection*{NASA Technical Memoranda}
\noindent

\years{1989}
Stone, L. S., Watson, A. B., and Mulligan, J. B., (1989).
\emph{Effect of contrast on the perception of direction of a moving pattern.}
NASA Tech. Memo. \#102234.\\

\years{1988}
Mulligan, J. B., and Stone, L. S., (1988),
\emph{Efficient use of bit planes in the generation of motion stimuli.}
NASA Tech. Memo. \#101022.\\

\noindent

\begin{center}
{\scriptsize  Last updated: \today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://nitens.org/taraborelli/cvtex}{
%\fontspec{Times New Roman}
\XeTeX } 
% put the two backslashes after the brace above if the cv pdf URL will follow...
%\\
% and then get rid of this brace...
}
% ---- FILL IN THE FULL URL TO YOUR CV HERE
% Stupid management took away my web server and won't let me post a pdf cv...
%\href{http://scanpath.arc.nasa.gov/jbm_cv}{http://scanpath.arc.nasa.gov/jbm_cv}}
%\href{http://nitens.org/taraborelli/cvtex}{http://nitens.org/taraborelli/cvtex}}
% can't have underscore?
%\href{http://scanpath.arc.nasa.gov/jbm/jbm\_cv.pdf}
%{http://scanpath.arc.nasa.gov/jbm\_cv.pdf}}
\end{center}

\end{document}
